\chapter{Installation}

\section{Environment Setup}
\begin{enumerate}
    \item We utilized \textbf{MacOS} as our testing environment.
    \item We cloned the repository and entered its folder.
    \begin{verbatim}
    git clone git@github.com:felixsrp/RojasJinLe.git
    cd RojasJinLe/
    \end{verbatim}
\end{enumerate}

\section{Backend Installation}
\begin{enumerate}
    \item We moved into the backend directory.
    \begin{verbatim}
    cd backend/
    \end{verbatim}
    \item We installed \textbf{Node.js} (v16.x) and \textbf{npm}.
    \item We installed \textbf{Docker Desktop} for MacOS.
    \item We ensured Docker was running and started the necessary containers.
    \begin{verbatim}
    docker compose up -d postgres adminer maildev
    \end{verbatim}
    \item We installed the backend dependencies.
    \begin{verbatim}
    npm install
    \end{verbatim}
    \item We copied the environment variables file.
    \begin{verbatim}
    cp .env.example .env
    \end{verbatim}
    \item We ran the database migrations.
    \begin{verbatim}
    npm run migration:run
    \end{verbatim}
    \item We populated the database with test data.
    \begin{verbatim}
    npm run seed:run:relational
    \end{verbatim}
    \item We started the backend server.
    \begin{verbatim}
    npm run start:dev
    \end{verbatim}
    \item We accessed the backend API at \textbf{http://localhost:3000}.
\end{enumerate}

\section{Frontend Installation}
\begin{enumerate}
    \item We downloaded and installed \textbf{Android Studio} from the official website.
    \item We launched the \textbf{Android Emulator} using the \textbf{Virtual Device Manager}.
    \item We installed the application by dragging and dropping the APK into the emulator.
    \item We verified that the application was launched correctly.
\end{enumerate}

\section{Conclusion}
The installation process proceeded smoothly without any issues.

