\chapter{Introduction}

\section{Purpose}

Students\&Companies (S\&C) is a platform designed to connect university students with companies offering internships.
It simplifies the internship searches of students and the projects advertisement for companies.

The platform employs recommendation mechanisms to match students and companies based on experience, skills, and project requirements.
S\&C also supports the selection process by managing interviews and collecting feedbacks.
Additionally, it provides suggestions for improving CVs and project descriptions.

\subsection{Goals}

\begin{enumerate}[label=\textbf{G\arabic* -}]
   \item Allow registered students to search and enroll for internship opportunities.
   \item Allow registered companies to advertise internship project opportunities.
   \item Allow registered universities to monitor their students ongoing internship and manage complaints.
   \item Support companies in the selection process by providing students with custom-made questionnaires.
   \item Ease matching by notifying students of relevant internships and companies for suitable candidates.
   \item Provide suggestions to both parties to refine their submissions.
\end{enumerate}

\section{Scope}

\subsection{Features}

\begin{enumerate}[label=\textbf{F\arabic* -}]
    \item Recommendation mechanism: students and companies are matched based on skills, experience and project requirements, exploiting keyword statistical methods.
    \item Internship search: students actively search and apply for internships, while also being notified of opportunities that align with their profile.
    \item Selection support: companies are helped in the selection process by setting up interviews, creating custom questionnaires, and finalizing selections.
    \item Suggestions system: suggestions are provided to both parties in order to improve CVs and project descriptions, to enhance match potential.
    \item Complaint management: universities can monitor internships of their students, handling complaints and addressing issues.
\end{enumerate}

\subsection{World phenomena}

\begin{enumerate}[label=\textbf{WP\arabic* -}]
    \item A student looks for an internship to which apply.
    \item A company advertises an open internship project.
    \item A student candidates himself for an internship.
    \item A company asks a matched student to fill a questionnaire.
    \item A company accepts a student for its internship project.
    \item A university wants to visualize its student ongoing internship data.
    \item A student or a company sends a compaint to the university.
\end{enumerate}

\subsection{Shared phenomena}

\begin{enumerate}[label=\textbf{SP\arabic* -}]

\subsubsection{Controlled by the machine}

    \item The system shows some internship advertisement to the student.
    \item The system shows some eligible student information to the company.
    \item The system notifies companies about students enrollment requests.
    \item The system notifies students about companies candidation offers.
    \item The system shows the company a panel in which to create a custom questionnaire.
    \item The system shows the student the questionnaire to fill.
    \item The system assigns the student to an internship project of a company.
    \item The system notifies a student or a company with a suggestion.
    \item The system notifies the university of a complaint.
    \item The system ends the internship of a student.

\subsubsection{Controlled by the world}

    \item A student fills the form with its personal data and uploads its CV.
    \item A company fills the form for advertising an internship project.
    \item A student sends an enrollment request for an internship project.
    \item A company sends an enrollment suggestion to a student.
    \item A company creates a custom questionnaire.
    \item A company sends a questionnaire to a student.
    \item A student fills a questionnaire a company sent.
    \item A company accepts a candidate student for its internship project.
    \item A student or a company sends a complaint to the university.
    \item A university ends the internship of its student.

\end{enumerate}

\section{Definitions, acronyms, abbreviations}

\section{Revision history}

\section{Reference documents}

\section{Document structure}
