\chapter{Overall description}

\section{Product perspective}

\subsection{Scenarios}

\begin{enumerate}[label=\textbf{S\arabic* -}]
    \item Signing up and logging in
    \item Filling in personal information
    \item Uploading the CV
    \item Creating an internship project advertisement
    \item Notifying the availability of an internship
    \item Selecting an internship project
    \item Creating a custom questionnaire
    \item Filling a questionnaire
    \item Starting a new internship
    \item Viewing internship information
    \item Sending a complaint
    \item Ending an internship
\end{enumerate}

\section{Product functions}

\subsection{Key functions}

\begin{enumerate}[label=\textbf{KF\arabic* -}]
    \item Internship project advertisements
    \item CV upload
    \item Interviews via custom questionnaires
    \item Complaints management
    \item Recommendation system
    \item Suggestion system
\end{enumerate}

\subsection{Requirements}

\begin{enumerate}[label=\textbf{R\arabic* -}]
    \item The system must allow an unregistered student to sign up.
    \item The system must allow an unregistered company to sign up.
    \item The system must allow an unregistered university to sign up.
    \item The system must allow a registered user to log in.
    \item The system must allow a registered user to fill in and edit its personal information.
    \item The system must allow a registered student to upload its CV.
    \item The system must allow a registered company to post an internship project.
    \item The system must allow a registered student to visualize a list of open internship projects.
    \item The system must allow a registered company to visualize a list of eligible students.
    \item The system must allow a registered student to make and enrollment request to an internship project.
    \item The system must allow a registered company to build custom made questionnaires.
    \item The system must allow a registered company to send questionnaires to students.
    \item The system must allow a registered student to fill in the questionnaire.
    \item The system must allow a registered company to accept students enrollment requests.
    \item The system must allow a registered student to see their ongoing internship information.
    \item The system must allow a registered company to see their ongoing internships information.
    \item The system must allow a registered university to see their students' ongoing internship information.
    \item The system must allow a registered student to send complaints to the university.
    \item The system must allow a registered company to send complaints to the university.
    \item The system must allow a registered university to visualize complaints it received.
    \item The system must allow a registered university to end an ongoing internship of its student.
\end{enumerate}

\section{User characteristics}

\section{Assumptions, dependencies and constraints}

\subsection{Domain assumptions}

\begin{enumerate}[label=\textbf{D\arabic* -}]
    \item The user must have a working internet connection.
    \item The user must have provided valid personal information.
    \item The student must be registered to a university.
    \item The university must have provided an organization mail to the student.
\end{enumerate}
