\chapter{Product functions and requirements}

\section{Product functions}

\subsection{Key functions}

\begin{enumerate}[label=\textbf{KF\arabic* -}]
    \item \textbf{Internship project advertisements -}
    Implemented - Companies can post detailed internship project descriptions, including tasks, required skills, technologies, and terms like compensation and benefits.
    This provides students clear insights about the available opportunities.
    \item \textbf{CV upload -}
    Implemented - Students can upload and manage their CVs, listing skills, experiences, and interests.
    This helps the system match students with suitable internships and allows companies to view candidate profiles.
    \item \textbf{Interviews via custom questionnaires -}
    Partially implemented: questionnaires come in the form of a single question with the relative answer - S\&C supports the interview process by allowing companies to set up structured questionnaires, enabling them to gather specific information from candidates and assess their compatibility with the internship.
    \item \textbf{Complaints management -}
    Not implemented - The platform includes a complaints management feature where students and companies can report issues to the university, that can then address is accordingly, ensuring smooth and fair handling of internship-related problems.
    \item \textbf{Recommendation system -}
    Implemented - S\&C employs a recommendation system that connects students with internships based on CV content and project requirements, using keyword matching statistical analyses, to optimize matches.
    \item \textbf{Suggestion system -}
    Not implemented - The platform provides guidance for students and companies on improving their CVs and project descriptions, enhancing their appeal and increasing the likelihood of successful matches.
\end{enumerate}

\section{Requirements}

\begin{enumerate}[label=\textbf{R\arabic* -}]
    \item Implemented - The system must allow an unregistered student to sign up.
    \item Implemented - The system must allow an unregistered company to sign up.
    \item Not implemented - The system must allow an unregistered university to sign up.
    \item Implemented - The system must allow a registered user to log in.
    \item Implemented - The system must allow a registered user to fill in and edit its personal information.
    \item Implemented - The system must allow a registered student to upload its CV.
    \item Implemented - The system must allow a registered company to post an internship project.
    \item Implemented - The system must allow a registered student to visualize a list of open internship projects.
    \item Implemented - The system must allow a registered company to visualize a list of eligible students.
    \item Implemented - The system must allow a registered student to make an enrollment request to an internship project.
    \item Partially implemented - The system must allow a registered company to build custom made questionnaires.
    \item Partially implemented - The system must allow a registered company to send questionnaires to students.
    \item Partially implemented - The system must allow a registered student to fill in the questionnaire.
    \item Implemented - The system must allow a registered company to accept students enrollment requests.
    \item Implemented - The system must allow a registered student to see their ongoing internship information.
    \item Implemented - The system must allow a registered company to see their ongoing internships information.
    \item Not implemented - The system must allow a registered university to see their students ongoing internship information.
    \item Not implemented - The system must allow a registered student to send complaints to the university.
    \item Not implemented - The system must allow a registered company to send complaints to the university.
    \item Not implemented - The system must allow a registered university to visualize complaints it received.
    \item Not implemented - The system must allow a registered university to end an ongoing internship of its student.
    \item Implemented - The system must allow a registered student to fill in a feedback form when the internship ends.
    \item Implemented - The system must allow a registered company to fill in a feedback form when the internship ends.
    \item Implemented - The system must allow a registered student to visualize a list of suggested internships.
    \item Implemented - The system must allow a registered company to visualize a list of suggested students.
    \item Implemented - The system must allow a registered student to be notified about recommended internship.
    \item Not implemented - The system must allow a registered company to be notified about recommended students.
\end{enumerate}


